E Coli Project Paper Incredibly Rough Draft

### 2013-08-28 paper/paper.tex

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of a 5$\mu m$ by 1$\mu m$ pill shaped cell (above) and a
    3$\mu m$ by 1$\mu m$ pill shaped cell (below).  The vertical axis shows
    stacked the total number of proteins that are of four different
    compound stages and in the right section of the cell (bottom four
    colors), in the middle of the cell (middle four colors) and in the
    left section of the cell (top four colors). The different forms of
    protein changes while the total number of MinD protein in the cell
    remains constant, shown by the fact that the very top line is
    horizontal.}
  \label{total-oscillation-plot}
\end{figure}

@@

\subsection{Randst shape}
\subsubsection{Randst-96-Star}
\subsubsection{Randst-97-}
\subsubsection{Randst-98-Actually Random}
\subsubsection{Randst-99}
\section{Interpretation of Data}
\section{Conclusion}
\section*{Appendix}
\bibliography{paper}

>>>>

\begin{figure}
  %%\includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-400-50-0-0-1500}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-200-50-0-0-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of a 5$\mu m$ by 1$\mu m$ pill shaped cell (above) and a
    3$\mu m$ by 1$\mu m$ pill shaped cell (below).  The vertical axis shows
    stacked the total number of proteins that are of four different
    compound stages and in the right section of the cell (bottom four
    colors), in the middle of the cell (middle four colors) and in the
    left section of the cell (top four colors). The different forms of
    protein changes while the total number of MinD protein in the cell
    remains constant, shown by the fact that the very top line is
    horizontal.}
  \label{total-oscillation-plot}
\end{figure}

@@

\subsection{Triangular Shapes}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-500-300-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-360-480-600-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of a equilateral (top), iscoscolese (middle), and 3-4-5
    (bottom) triangle.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{total-oscillation-triangle-plot}
\end{figure}

Figure \ref{total-oscillation-triangle-plot} shows the equivalent
motion and transference between compound states for the triangular
states as Figure \ref{total-oscillation-plot} does for the pill shaped
cells.  The equilateral triangular shows that in all three sections
there is a spike in wall attached MinD-ATP directly followed by a
spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
pattern except that the mid section exhibited no such pronounced
spike.  Interestingly, the right and mid sections show spikes at
similar times when compared to the left section spikes, which seem to
oscillate in a manner shifted pi off from the other two.  This
behavoir shows itself in the animations, which show a relaxation into
a stable oscillation from a maxima in one corner to a double maxima in
the other two corners, and back again.  The left section heights are
roughly twice that of the right section heights.  The simulations are
started with higher concentrations of proteins in primarily the right
section, with some overlap into the middle section, so that perhpas
this oscillation pattern seems reasonable.  However, it's interesting
to note that the oscillations, started with assymmetric density, do
not naturally rotate around the corners of the triangle in a circular
pattern.

It seems as well that there is a desired oscillation maxima for the
particular shape and size of the cell, as can be seen by the
relaxation, over the first four periods, to a regular maximal height
of the right and left sections' total protein at the height of each spike.

\fixme{Note to make sure I'm interpreting the iscosolese triangle data
  correctly: the triangle sides are 5,5,3, and the higher density
  starts in the corner that is opposite the short side.  This corner
  is covered by the right section.  I've verified this by looking at
  the protein_microscopy and drawing a little picture, which is on my
  desk...if you dare look for something on my desk!!!}  The iscosolese
triangle starts its simulation with a higher concentration of protein
in the section that is opposite the shorter side.  It quickly relaxes
into a stable oscillation pattern.  This pattern shows that right
corner section regularly has higher spikes in total protein than the
other sections, and that its spikes appear one pi removed from the
spikes for the other two sections.  This a similar behavoir to that
which is seen in the equilateral triangle, differening in that it
converges more quickly towards this behavoir and that it shows a
greater exageration in the height of protein buildup in the right most
section.

\fixme{Note on interpretation of 3-4-5 triangle: the higher density
  starts to the right of a vertical line that is parrallel to the
  second longest side in the triangle (the longer of the two
  non-hypotonuse sides).  This means the higher concentration covers
  the right angle and also the smaller angle in the triangle} The
3-4-5 triangle exhibits behavoir that I need more data to properly
observe.  I does not converge as quickly as that for the iscosolese or
equilateral triangles.

\subsection{Randst shape}
\fixme{Cheat sheet for the shapes, need to put these into a big figure
  from the sections output: 96=star shape, 97=sideways sideways
  flying saucer pancake, 98=manniks squished cell, 99=an A}

\begin{figure}

\end{figure}
\subsubsection{Randst-96-Star}
The animations seem to relax into a pattern in which the oscillations
go from the smallest corner, out to the other three, and then back to
the smallest corner.  \fixme{There isn't enough data to see properly
  though, need to run for longer.}

\subsubsection{Randst-97-}
The sideways flying saucer pancake shape shows a truly interesting
breakdown of an unstable equilibrium oscillation.  For the first
number of oscillations the maxima trade off right to left, from a high
peak in the leftward compartment to vertically opposed peaks in the
poles of the long axis of the cell.  This is perhaps due to the fact
that the starting density is highly concentrated to the right of a
dividing line that runs parrallel to the right vertical side.  After a
few oscillations the back and forth oscillations tip toward the
vertical direction and the system loses its initial oscillation
pattern.

\subsubsection{Randst-98-C-Reminiscent of Mannik's cell}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-800-9800-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the manniks squished cell
    shape.  The vertical axis shows stacked the total number of
    proteins that are of four different compound stages and in the
    different sections of the cell.}
  \label{total-oscillation-randst-98-plot}
\end{figure}

Our animations and total protein fluctuation plots (Figure
\ref{total-oscillation-randst-98-plot} for our C shape (reminiscent of
the flattened cell shown in Mannik's work) shows a very regular,
stable, simple oscillation pattern.  There are two clear ends of this
cell that oppose one another, and the protein maximum travels to one
end, where it reaches a peak, then travels through the cell to the
other end, reaching another peak, and then repeats the process.  In a
way it is similar to the simple pill shapes, in that there are two
clear endcaps and a middle section (that is in this case bends and
curves).  The protein fluctuation plots show our familiar pattern of
high spikes in wall attached MinD-ATP immediately followed by spikes
in wall attached MinD-MinE-ATP, followed by a drop in both as the
proteins move towards the other side.

\subsubsection{Randst-99 our A shape}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the A shaped shape.  The vertical axis shows stacked the total number
    of proteins that are of four different compound stages and in the
    different sections of the cell.}
  \label{total-oscillation-randst-96-plot}
\end{figure}
Our animations for this plot show a very interesting pattern.  The
maxima oscillates from the right corner to the top corner, then
\emph{back to the right corner} then to the top corner again, then to
the left corner, then back to the top, then to the left, then to the
top again, then back to the right side.  It's fascinating that there
must be two back and forth motions before proceeding to the other side
\fixme{would this happen over and over or would there be a chaos,
  breakdown sort of thing at some point.  Need longer sim}.  The total
fluctuation plot shows this double maxima corner pattern, with two
spikes on the right, then two spikes on the left, then two back on the
right.

\section{Interpretation of Data}
\section{Conclusion}
\section*{Appendix}
\bibliography{paper}
